Statistical methods for relative quantification of post-translational modifications in global proteomics experiments

### 2021-09-24 supplementary/ptm_sm.tex
cleaned up supplementary, added minor updates to main

\usepackage{geometry}
%\usepackage{amsmath}
%\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{rotating}
\usepackage{color}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,backgrounds,calc,positioning,fit,petri,plotmarks}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{url}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{authblk}

@@

\paragraph{Data structure of PTM quantification experiments.}
A set of fully-cleaved and/or partially-cleaved peptides containing a same PTM (e.g., ubiquitination/phosphorylation) at one site are considered together. There are $I$ conditions and $J$ mass spectrometry runs (technical replicates) per condition in the experiment. The PTM site is represented by $K$ spectral features (peptide ions, distinguished by their cleavage residues and charge states). The log-intensity (base 2) of Feature $k$, in Run $j$ of Condition $i$ is denoted by $y_{ijk}$. To account for the underlying protein abundance, features corresponding to the unmodified peptides from the same protein are considered together, except those unmodified peptides containing a modified site to avoid the confounding effect due to the PTM. The log-intensity of Feature $l$ from the unmodified peptides in the same run is denoted by $y_{ijl}^{\ast}$. \sfigref{fig:dtable} shows an example data representation of modified peptide ions at one site and unmodified peptide ions of the same protein. Unmodified peptides from the same protein provide additional evidence on the underlying protein abundance, which needs to be integrated for PTM characterization. To address the goals of PTM characterization, statistical analysis needs to summarize values in this table using appropriate statistical models, translate the goal into a model-based quantity of interest, and draw inference (i.e., characterize the uncertainty) about the quantity.

@@

Limma uses linear models to test the null hypothesis that there is no difference in mean PTM abundances between conditions. Additionally it leverages Empirical Bayes moderation to share pooled variance information across individual modification models and moderate the individual residual variances. Using a linear model allows Limma to share variance information across conditions, providing a more accurate estimate.

@@

@@

The methods described previously can be extrapolated to Tandem Mass Tag (TMT) experiments targeting PTMs. The null hypothesis is that there is no difference in mean PTM abundance between Conditions $i$ and $i'$ after adjusting for changes in mean unmodified peptide abundance between Conditions $i$ and $i'$. 
\begin{align*}
H_{0}: \Delta = (\mu_{i} - \mu_{i'}) - (\mu_{i}^{\ast} - \mu_{i'}^{\ast}) &= 0 \\
H_{a}: \Delta = (\mu_{i} - \mu_{i'}) - (\mu_{i}^{\ast} - \mu_{i'}^{\ast}) &\neq 0
\end{align*}

For TMT experiments there is an additional source of variation coming from the mixtures used. This increases the complexity as there are many options for allocating samples to mixtures, including multiple mixtures, biological replicates, and technical replicates. Going forward we will denote the log-intensity of a modified peptide for Technical Replicate j of Mixture m for Condition i by $y_{ijm}$, where $m = 1,....,M$. This is done in the same way for the unmodified peptide $y^*_{ijm}$.

@@

\begin{align*}
Y_{mtcb} = \mu + Mixture_m + Techrep(Mixture)_{jm} + Condition_c + Subject_{mcb} + \epsilon_{mtcb}\\
Y^*_{mtcb} = \mu^* + Mixture^*_m + Techrep(Mixture)^*_{jm} + Condition^*_c + Subject^*_{mcb} + \epsilon^*_{mtcb}
\end{align*}

Where $Mixture_m \sim N(0, \sigma^2_m)$, $Techrep(Mixture)_{jm} \sim N(0, \sigma^2_{jm})$, $Subject \sim N(0, \sigma^2_{s})$ are random effects, and $\sum_{c=1}^{I} Condition_{c}^{\ast} = 0$ is a fixed effect. Finally the error is expressed as $\epsilon_{mtcb} \sim N(0, \sigma^2)$.

@@

The results are summarized from \sfigref{fig:prot_fpr} to \sfigref{fig:fc_boxplot}, including false discovery rate with or without changes in protein abundance by the considered methods (\sfigref{fig:prot_fpr}), false positive rate, and overall accuracy. Additionally the results are compared to simulation 2 described in the next section.

@@

The results are summarized from \sfigref{fig:sim1_fpr} to \sfigref{fig:fc_boxplot}, including false positive rate with or without changes in protein abundance by the considered methods (\sfigref{fig:sim1_fpr}), false positive rate, and overall accuracy. Again the results are compared to simulation 1.

@@

\begin{figure}[h!]
\centering
 \begin{subfigure}{.9\textwidth}
	\includegraphics[width=.9\textwidth]{sim_new/sim1_FDR_all_models}\\
	\caption{All the considered methods in simulation 1 correctly calibrated FDR rate when adjusting for changes in protein abundance. In comparison, the methods without accounting for the protein-level changes resulted in off-target, high false positive rates.}
 \end{subfigure}
 \begin{subfigure}{.9\textwidth}
	\includegraphics[width=.9\textwidth]{sim_new/sim1_FDR}
	\caption{The considered methods with protein adjustment are compared in detail. All three methods generally performed similarly in terms of FDR.}
 \end{subfigure}
\label{fig:sim1_fpr}
\end{figure}

\begin{figure}[h!]
\centering
 \begin{subfigure}{.9\textwidth}
	\includegraphics[width=.9\textwidth]{sim_new/sim1_Recall}\\
	\caption{The recall(false positive rate) for simulation 1 methods with adjustment were compared. It is clear that Limma performs the strongest here when the number of replicates were low.  At higher replicates the performance of the proposed methods and Limma are comparable. T-test clearly performs worse across all methods.}
 \end{subfigure}
 \begin{subfigure}{.9\textwidth}
	\includegraphics[width=.9\textwidth]{sim_new/sim1_accuracy}
	\caption{The overall accuracy plot mimics the observations in the recall plot. Limma performs stronger than the proposed method at lower replicates, while at higher they are comparable.}
 \end{subfigure}
\label{fig:sim1_recall}
\end{figure}

\begin{figure}[h!]
\centering
 \begin{subfigure}{.9\textwidth}
	\includegraphics[width=.9\textwidth]{sim_new/sim3_Recall}
	\caption{The advantage of using the proposed approach is apparent when looking at simulation 2, which includes limited observations and the presence of missing values. In the case of recall the proposed method performs stronger than limma and t-test in nearly every model. Even at lower replicates the proposed method still outperformed limma, especially when there were more conditions in the simulation. Again the lowest performance was observed using the $t$-test method.}
 \end{subfigure}
 \begin{subfigure}{.9\textwidth}
	\includegraphics[width=.9\textwidth]{sim_new/sim3_Accuracy}
	\caption{The overall accuracy plots show similar results to recall. The proposed method performed the strongest across all methods, even when replicates were low. Limma shows strong performance in a clean experiment, when real world data problems are introduced it is clear the proposed method is more robust.}
 \end{subfigure}
\label{fig:sim2_recall}
\end{figure}

\begin{figure}[h!]
\centering
 \begin{subfigure}{.9\textwidth}
	\includegraphics[width=.9\textwidth]{sim_new/sim1_FC_boxplot}
	\caption{In simulation 1 all considered methods correctly estimated the fold change between conditions, with a median fold change estimation of .75 in all methods. The distributions around the median were also consistent acorss all methods. Predictably the distribution quantiles decrease as the number of replicates increases.}
 \end{subfigure}
 \begin{subfigure}{.9\textwidth}
	\includegraphics[width=.9\textwidth]{sim_new/sim3_FC_boxplot}
	\caption{In simulation 2 again all methods correctly estimated the fold change with a median log change of .75. The proposed method in this simulation had a visibly tighter distribution around the median. Both Limma and $t$-test showed a wider range around the fold change. In this case the proposed method showed a stronger performed in correctly estimating the fold change for all peptides.}
 \end{subfigure}
\label{fig:fc_boxplot}
\end{figure}

@@

\begin{figure}[h!]
\centering
 \begin{subfigure}{\textwidth}
	\includegraphics[width=\textwidth]{sim_new/IpaH_prof_plot}
	\caption{Comparing the global profiling of protein $GSDMD\_HUMAN|P57764$ with the ubiquitination of the protein at site $K62$. The individual PSM features are shown in grey, while the feature summarization is shown in red. When looking at the summary of the modification and global protein it is clear the conditions follow different trends. Specifically, there appears to be no change in abundance between Dox1hr and Dox4hr in the modified plot, however there is a large negative change when looking at the unmodified plot. This indicates the modification is confounded with changes in the unmodified protein.}
 \end{subfigure}
 \begin{subfigure}{\textwidth}
	\includegraphics[width=\textwidth]{sim_new/IpaH_volcano_plot}
	\caption{Volcano plots of Dox4hr vs Dox1hr both before and after protein adjustment. The $GSDMD\_HUMAN|P57764\_K62$ modification is highlighted. Before adjustment the modification has a small fold change and insignificant adjusted pvalue. After adjustment the fold change is much larger and the adjusted pvalue is very significant. In this case the proposed method allows us to identify differential modified peptides that could have otherwise been missed.}
 \end{subfigure}
\label{fig:ipah_figures}
\end{figure}

@@

\begin{figure}[h!]
\centering
 \begin{subfigure}{\textwidth}
	\includegraphics[width=\textwidth]{sim_new/No_Difference_Shigella_Profile_Plot}
	\caption{Comparing the global profiling of protein $TTP\_MOUSE|P22893$ with the modification of the protein at site $S178$. The individual PSM features are shown in grey, while the feature summarization is shown in red. When looking at the summary of the modification and global protein it is clear the difference between conditions follow the same trend. Specifically, there is a positive adjustment in abundance when comparing WT\_Uninfect to WT\_Late in both the modification and global profiling run. This indicates the movement is driven by changes in global protein.}
 \end{subfigure}
 \begin{subfigure}{\textwidth}
	\includegraphics[width=\textwidth]{sim_new/No_Difference_Shigella_Volcano}
	\caption{Volcano plots of WT\_Late vs WT\_Uninfect both before and after protein adjustment. The $TTP\_MOUSE|P22893\_S178$ modification is highlighted. Before adjustment the modification has a large fold change and significant adjusted pvalue. After adjustment the fold change is much smaller and the adjusted pvalue is insignificant.}
 \end{subfigure}
\label{fig:No_Diff_Shigella_PTM}
\end{figure}

\begin{figure}[h!]
\centering
 \begin{subfigure}{\textwidth}
	\includegraphics[width=\textwidth]{sim_new/Difference_Shigella_Profile_Plot}
	\caption{Comparing the global profiling of protein $KI67\_MOUSE|E9PVX6$ with the modification of the protein at site $T215$. In this case the modification and global protein trend in different directions. Specifically, comparing WT\_Uninfect and WT\_Early there is a slightly positive change in abundance, however in the global profiling there was a negative change. In this case the profile plot indicates the effect of the modification is masked by the change in global protein abundance. Additionally this profile plot shows the large difference in available features between modifications and global protein.}
 \end{subfigure}
 \begin{subfigure}{\textwidth}
	\includegraphics[width=\textwidth]{sim_new/Difference_Shigella_Volcano}
	\caption{Volcano plots of WT\_Early vs WT\_Uninfect both before and after protein adjustment. The $KI67\_MOUSE|E9PVX6$ modification is highlighted. Before adjustment the modification has a small positive fold change and insignificant adjusted pvalue. After adjustment the fold change increases and the adjusted pvalue is now significant.}
 \end{subfigure}
\label{fig:Diff_Shigella_PTM}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{sim_new/simple_power_analysis}
\caption{The number of replicates per condition required to reach a power of .9 can be seen in the plot. At a high standard deviation and low expected fold change the number of replicates is unrealistically high. As the expected fold change increases the number of replicates needed decreases dramatically. The standard deviation of .1 expectantly shows the least number of replicates needed regardless of fold change.}
\label{fig:sample_size}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{sim_new/power_analysis_sd_combined}
\caption{When the unmodified peptide has a low standard deviation the number of replicates is very similar to the baseline. As the standard deviation increases the number of replicates increases greatly. When the unmodified stand deviation is much higher than the modified, we can see that many more replicates are needed to reach the same power.}
\label{fig:power_sd_combo}
\end{figure}

@@

\bibliographystyle{plain}
\bibliography{ptm_ref}

>>>>

\usepackage{geometry}
%\usepackage{amsmath}
%\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{rotating}
\usepackage{color}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,backgrounds,calc,positioning,fit,petri,plotmarks}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{url}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{authblk}
\usepackage[backend=biber]{biblatex}
\bibliography{ptm_ref}

@@

\subsection{Data structure of PTM quantification experiments.}
A set of fully-cleaved and/or partially-cleaved peptides containing a same PTM (e.g., ubiquitination/phosphorylation) at one site are considered together. There are $I$ conditions and $J$ mass spectrometry runs (technical replicates) per condition in the experiment. The PTM site is represented by $K$ spectral features (peptide ions, distinguished by their cleavage residues and charge states). The log-intensity (base 2) of Feature $k$, in Run $j$ of Condition $i$ is denoted by $y_{ijk}$. To account for the underlying protein abundance, features corresponding to the unmodified peptides from the same protein are considered together, except those unmodified peptides containing a modified site to avoid the confounding effect due to the PTM. The log-intensity of Feature $l$ from the unmodified peptides in the same run is denoted by $y_{ijl}^{\ast}$. \sfigref{fig:dtable} shows an example data representation of modified peptide ions at one site and unmodified peptide ions of the same protein. Unmodified peptides from the same protein provide additional evidence on the underlying protein abundance, which needs to be integrated for PTM characterization. To address the goals of PTM characterization, statistical analysis needs to summarize values in this table using appropriate statistical models, translate the goal into a model-based quantity of interest, and draw inference (i.e., characterize the uncertainty) about the quantity.

@@

Limma uses linear models to test the null hypothesis that there is no difference in mean PTM abundances between conditions. Additionally, it leverages Empirical Bayes moderation to share pooled variance information across individual modification models and moderate the individual residual variances. Using a linear model allows Limma to share variance information across conditions, providing a more accurate estimate.\cite{Ritchie_15a}

@@

After fitting a linear model, the final variance is moderated using Empirical Bayes and the global variance across all modified peptides. This is done as $s_{i} = P(v_i| v_\Theta)$ where $v_i$ is the resulting variance when modeling peptide $i$ and $v_\Theta$ is the global variance.

@@

The methods described previously can be extrapolated to Tandem Mass Tag (TMT) experiments targeting PTMs, similarly to how MSstatsTMT targets the global protein.\cite{Huang:2020} The null hypothesis is still that there is no difference in mean PTM abundance between Conditions $i$ and $i'$ after adjusting for changes in mean unmodified peptide abundance between Conditions $i$ and $i'$. 
\begin{align*}
H_{0}: \Delta = (\mu_{i} - \mu_{i'}) - (\mu_{i}^{\ast} - \mu_{i'}^{\ast}) &= 0 \\
H_{a}: \Delta = (\mu_{i} - \mu_{i'}) - (\mu_{i}^{\ast} - \mu_{i'}^{\ast}) &\neq 0
\end{align*}

For TMT experiments there is an additional source of variation coming from the mixtures used. This increases the model complexity as variation can now come from multiple mixtures, biological replicates, and technical replicates. Going forward we will denote the log-intensity of a modified peptide for Technical Replicate j of Mixture m for Condition i by $y_{ijm}$, where $m = 1,....,M$. This is done in the same way for the unmodified peptide $y^*_{ijm}$.

@@

\begin{align*}
Y_{mtcb} = \mu + Mixture_m + Techrep(Mixture)_{tm} + Condition_c + Subject_{mcb} + \epsilon_{mtcb}\\
Y^*_{mtcb} = \mu^* + Mixture^*_m + Techrep(Mixture)^*_{tm} + Condition^*_c + Subject^*_{mcb} + \epsilon^*_{mtcb}
\end{align*}

Where $Mixture_m \sim N(0, \sigma^2_m)$, $Techrep(Mixture)_{tm} \sim N(0, \sigma^2_{tm})$, $Subject \sim N(0, \sigma^2_{s})$ are random effects, and $\sum_{c=1}^{I} Condition_{c}^{\ast} = 0$ is a fixed effect. Finally the error is expressed as $\epsilon_{mtcb} \sim N(0, \sigma^2)$.

@@

The results are summarized from \sfigref{fig:sim1_fpr} to \sfigref{fig:sim1_recall}, including false discovery rate with or without changes in protein abundance by the considered methods, false positive rate, and overall accuracy. Additionally the results are compared to simulation 2 described in the next section.

@@

The results are summarized from \sfigref{fig:sim2_recall} to \sfigref{fig:fc_boxplot}, including false positive rate with or without changes in protein abundance by the considered methods, false positive rate, and overall accuracy.

@@

\begin{figure}[h!]
\centering
 \begin{subfigure}{\textwidth}
  \centering
	\includegraphics[width=.8\textwidth]{sim_new/sim1_FDR_all_models}\\
	\caption{All the considered methods in simulation 1 correctly calibrated FDR rate when adjusting for changes in protein abundance. In comparison, the methods without accounting for the protein-level changes resulted in off-target, high false positive rates.}
 \end{subfigure}
 \begin{subfigure}{\textwidth}
  \centering
	\includegraphics[width=.8\textwidth]{sim_new/sim1_FDR}
	\caption{The considered methods with protein adjustment are compared in detail. All three methods generally performed similarly in terms of FDR.}
 \end{subfigure}
 \caption{FDR of Simulation 1.}
\label{fig:sim1_fpr}
\end{figure}

\begin{figure}[h!]
\centering
 \begin{subfigure}{\textwidth}
  \centering
	\includegraphics[width=.8\textwidth]{sim_new/sim1_Recall}\\
	\caption{The recall(false positive rate) for simulation 1 methods with adjustment were compared. It is clear that Limma performs the strongest here when the number of replicates were low.  At higher replicates the performance of the proposed methods and Limma are comparable. T-test clearly performs worse across all methods.}
 \end{subfigure}
 \begin{subfigure}{\textwidth}
  \centering
	\includegraphics[width=.8\textwidth]{sim_new/sim1_accuracy}
	\caption{The overall accuracy plot mimics the observations in the recall plot. Limma performs stronger than the proposed method at lower replicates, while at higher they are comparable.}
 \end{subfigure}
\caption{Recall and Accuracy results of Simulation 1.}
\label{fig:sim1_recall}
\end{figure}

\begin{figure}[h!]
\centering
 \begin{subfigure}{\textwidth}
  \centering
	\includegraphics[width=.8\textwidth]{sim_new/sim3_Recall}
	\caption{The advantage of using the proposed approach is apparent when looking at simulation 2, which includes limited observations and the presence of missing values. In the case of recall the proposed method performs stronger than limma and t-test in nearly every model. Even at lower replicates the proposed method still outperformed limma. Again the lowest performaning method was $t$-test.}
 \end{subfigure}
 \begin{subfigure}{\textwidth}
  \centering
	\includegraphics[width=.8\textwidth]{sim_new/sim3_Accuracy}
	\caption{The overall accuracy plots show similar results to recall. The proposed method performed the strongest across all methods, even when replicates were low. Limma shows strong performance in a clean experiment, when real world data problems are introduced it is clear the proposed method is more robust.}
 \end{subfigure}
\caption{Recall and Accuracy results of Simulation 2.}
\label{fig:sim2_recall}
\end{figure}

\begin{figure}[h!]
\centering
 \begin{subfigure}{\textwidth}
 \centering
	\includegraphics[width=.8\textwidth]{sim_new/sim1_FC_boxplot}
	\caption{In simulation 1 all considered methods correctly estimated the fold change between conditions, with a median fold change estimation of .75. The distributions around the median were also consistent acorss all methods. Predictably the distribution quantiles decrease as the number of replicates increases.}
 \end{subfigure}
 \begin{subfigure}{\textwidth}
  \centering
	\includegraphics[width=.8\textwidth]{sim_new/sim3_FC_boxplot}
	\caption{In simulation 2 again all methods correctly estimated the fold change with a median log change of .75. The proposed method in this simulation had a visibly tighter distribution around the median. Both Limma and $t$-test showed a wider range around the fold change. In this case the proposed method showed a stronger performed in correctly estimating the fold change for all peptides.}
 \end{subfigure}
\caption{Fold change distribution comparison between Simulations 1 and 2.}
\label{fig:fc_boxplot}
\end{figure}

@@

\begin{figure}[h!]
\centering
 \begin{subfigure}{\textwidth}
 \centering
	\includegraphics[width=.9\textwidth]{sim_new/IpaH_prof_plot}
	\caption{Comparing the global profiling of protein $GSDMD\_HUMAN|P57764$ with the ubiquitination of the protein at site $K62$. The individual PSM features are shown in grey, while the feature summarization is shown in red. When looking at the summary of the modification and global protein it is clear the conditions follow different trends. Specifically, there appears to be no change in abundance between Dox1hr and Dox4hr in the modified plot, however there is a large negative change when looking at the unmodified plot. This indicates the modification is confounded with changes in the unmodified protein.}
 \end{subfigure}
 \begin{subfigure}{\textwidth}
 \centering
	\includegraphics[width=.9\textwidth]{sim_new/IpaH_volcano_plot}
	\caption{Volcano plots of Dox4hr vs Dox1hr both before and after protein adjustment. The $GSDMD\_HUMAN|P57764\_K62$ modification is highlighted. Before adjustment the modification has a small fold change and insignificant adjusted pvalue. After adjustment the fold change is much larger and the adjusted pvalue is very significant. In this case the proposed method allows us to identify differential modified peptides that could have otherwise been missed.}
 \end{subfigure}
\caption{Summary plots for modification of protein GSDMD at site K62.}
\label{fig:ipah_figures}
\end{figure}

@@

\begin{figure}[h!]
\centering
 \begin{subfigure}{\textwidth}
 \centering
	\includegraphics[width=.9\textwidth]{sim_new/No_Difference_Shigella_Profile_Plot}
	\caption{Comparing the global profiling of protein $TTP\_MOUSE|P22893$ with the modification of the protein at site $S178$. The individual PSM features are shown in grey, while the feature summarization is shown in red. When looking at the summary of the modification and global protein it is clear the difference between conditions follow the same trend. Specifically, there is a positive adjustment in abundance when comparing WT\_Uninfect to WT\_Late in both the modification and global profiling run. This indicates the movement is driven by changes in global protein.}
 \end{subfigure}
 \begin{subfigure}{\textwidth}
 \centering
	\includegraphics[width=.9\textwidth]{sim_new/No_Difference_Shigella_Volcano}
	\caption{Volcano plots of WT\_Late vs WT\_Uninfect both before and after protein adjustment. The $TTP\_MOUSE|P22893\_S178$ modification is highlighted. Before adjustment the modification has a large fold change and significant adjusted pvalue. After adjustment the fold change is much smaller and the adjusted pvalue is insignificant.}
 \end{subfigure}
\caption{Summary plots for modification of protein TTP at site S178.}
\label{fig:No_Diff_Shigella_PTM}
\end{figure}

\begin{figure}[h!]
\centering
 \begin{subfigure}{\textwidth}
 \centering
	\includegraphics[width=.9\textwidth]{sim_new/Difference_Shigella_Profile_Plot}
	\caption{Comparing the global profiling of protein $KI67\_MOUSE|E9PVX6$ with the modification of the protein at site $T215$. In this case the modification and global protein trend in different directions. Specifically, comparing WT\_Uninfect and WT\_Early there is a slightly positive change in abundance, however in the global profiling there was a negative change. In this case the profile plot indicates the effect of the modification is masked by the change in global protein abundance. Additionally this profile plot shows the large difference in available features between modifications and global protein.}
 \end{subfigure}
 \begin{subfigure}{\textwidth}
 \centering
	\includegraphics[width=.9\textwidth]{sim_new/Difference_Shigella_Volcano}
	\caption{Volcano plots of WT\_Early vs WT\_Uninfect both before and after protein adjustment. The $KI67\_MOUSE|E9PVX6$ modification is highlighted. Before adjustment the modification has a small positive fold change and insignificant adjusted pvalue. After adjustment the fold change increases and the adjusted pvalue is now significant.}
 \end{subfigure}
 \caption{Summary plots for modification of protein KI67 at site T215.}
\label{fig:Diff_Shigella_PTM}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=.9\textwidth]{sim_new/simple_power_analysis}
\caption{The number of replicates per condition required to reach a power of .9 can be seen in the plot. At a high standard deviation and low expected fold change the number of replicates is unrealistically high. As the expected fold change increases the number of replicates needed decreases dramatically. The standard deviation of .1 expectantly shows the least number of replicates needed regardless of fold change.}
\label{fig:sample_size}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=.9\textwidth]{sim_new/power_analysis_sd_combined}
\caption{When the unmodified peptide has a low standard deviation the number of replicates is very similar to the baseline. As the standard deviation increases the number of replicates increases greatly. When the unmodified stand deviation is much higher than the modified, we can see that many more replicates are needed to reach the same power.}
\label{fig:power_sd_combo}
\end{figure}

@@

\printbibliography
